---
title: "Spotify Songs"
description: |
  Analysis of Spotify Songs from TidyTuesday
author: Molly Liao
date: September 29, 2026
format:
  html:
    code-fold: true
    code-tools: true
    source: true
    code-overflow: wrap
execute: 
  warning: false
  message: false
---
**Data Source:** 
Data Science Learning Community. (2020). *Tidy Tuesday: 2020-01-21*. TidyTuesday. [GitHub](https://github.com/rfordatascience/tidytuesday/tree/main/data/2020/2020-01-21)


**Original data source / spotifyr:**
Thompson, C., Parry, J., Phipps, D., & Wolff, T. (2020). *spotifyr: R wrapper for the Spotify Web API.*  [spotifyr](https://www.rcharlie.com/spotifyr/)

The boxplot shows the popularity rating of different genre on Spotify. Pop music followed by latin music have popularities just over 50, while EDM has the lowest popularity. 

```{r}
library(tidyverse)
library(ggplot2)
spotify_songs <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/main/data/2020/2020-01-21/spotify_songs.csv')
view(spotify_songs)
```


```{r}
ggplot(
  spotify_songs, 
  aes(
    x = reorder(playlist_genre, track_popularity, FUN = median),
    y = track_popularity))+
    geom_boxplot()+
    labs(x = "Playlist genre",
    y = "Popularity",
    title = "Popularity by playlist genre")
```

