---
title: "Squirrels in Central Park"
description: |
  Analysis of Central Park Squirrel Census data from TidyTuesday
author: Molly Liao
date: September 29, 2026
format:
  html:
    code-fold: true
    code-tools: true
    source: true
    code-overflow: wrap
execute: 
  warning: false
  message: false
---
**Data Source:**
Data Science Learning Community. (2023). *Tidy Tuesday: 2023-05-23*. TidyTuesday. [GitHub](https://github.com/rfordatascience/tidytuesday/tree/main/data/2023/2023-05-23)
 

**Original data source:**
 NYC Open Data. (2018). *2018 Central Park Squirrel Census – Squirrel Data*. City of New York. [NYC Open Data](https://data.cityofnewyork.us/Environment/2018-Central-Park-Squirrel-Census-Squirrel-Data/vfnx-vebw/about_data)

The scatterplot illustrates the location squirrels were spotted in Central Park. They were mostly adults squirrels with a few juveniles. One thing to note on the graph is the empty space in the middle of the park, which is the where the lake is located, hence, no squirrels were spotted.   

```{r}
library(tidyverse)
library(ggplot2)
squirrel_data <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/main/data/2023/2023-05-23/squirrel_data.csv')
view(squirrel_data)
```

```{r}
squirrel_data <- squirrel_data |> 
  filter(Age %in% c("Adult", "Juvenile"))
```

```{r}
ggplot(squirrel_data, aes(x = X, y = Y, color = Age))+
  geom_point(
    size = 1,
    alpha = 0.3)+
  labs(
    x = "Longtitude",
    y = "Latitude",
    title = "Adults and Juvenile Squirrels Sighted in Central Park")
```